Results from the deep learning challenge associated with the 3MD4040 lecture on plankton classification

### 2022-08-16 Report/paper.tex
rm useless comment
last team descriptions

			\\
			\hline
			CelestineFeuillat & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			LesJongleurs & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			DeepBeru4s & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			The Whale Sharks & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
		\end{tabular}
			\caption{Overview of the experiments of the participants. Part 3. \label{table:overview3}}
	\end{table}
	\end{landscape}
	\clearpage
}

@@

%TODO : check why the off diagonal elements class do not match the badly classified classes listed above. There seems to be issues for class 11 for example ..

>>>>

			\\
			\hline
			CelestineFeuillat & 
				Resize($224$), RandAugment(num\_ops=4, magnitude=7, fill=255), ImageNet normalize 
			& None 
			& None
			& LinearNet, custom CNN, torchvision pretrained resnet18, resnet50
				& Weighted cross entropy() loss, Adam($0.001$),early stopping on validation F1, train/valid random split ($0.9, 0.1$), batch size $128$
				&class weights in the CE loss $w_k=\frac{\sum_i count_i}{86 count_k})$,
			\\
			\hline
			LesJongleurs & 
			Resize($224$), Normalize($0.5$, $0.5$) 
			&  None
			& None
			& LinearNet, torchvision pretrained resnet18, resnet50 
			& weighted cross entropy, Adam($0.001$), early stopping on validation F1, train/valid random split ($0.8, 0.2$)
			&class weights in the CE loss $w_k=\frac{\sum_i count_i}{count_k})$,
			\\
			\hline
			DeepBeru4s & 
			Resize($256$), CenterCrop($224$), Resize($256$), ImageNet Normalize 
			& HFlip ($0.5$), RandomRotate ($-15,15$)
			& HFlip ($0.5$), RandomRotate ($-15,15$)
			&  Linear, custom CNN, torchvision pretrained resnet34, resnet50, resnet152 with a possibly frozen backbone
				& weighted cross entropy loss or F1 loss\footnote{actually incorrectly coded}, Adam($0.001$), early stopping on validation weighted cross entropy, train/valid  random split ($0.8, 0.2$), batch size $128$ 
			&class weights in the CE loss $w_k=\frac{86}{count_k})$,batch sampler with $f_k = 1/count_k$
			\\
			\hline
			The Whale Sharks 
				& Invert, CenterCrop($300$) or Resize($300$), Normalize($0.013$,$0.0546$)
				& HFlip($0.5$), RandomRotate, Blur,
			& None
			& custom CNN, torchvision pretrained resnet101, resnet152, vgg16, vgg19
				& cross entropy loss or micro average F1 loss, Adam($0.001$), early stopping on the batch averaged micro average F1, train/valid random split ($0.8, 0.2$), batch size $256$ 
				& batch sampler with $f_k = 1/count_k$
			\\
		\end{tabular}
			\caption{Overview of the experiments of the participants. Part 3. \label{table:overview3}}
	\end{table}
	\end{landscape}
	\clearpage
}

@@
